Inquires in Racial and Sexual Disparities among Chicago Police Department

### 2024-02-15 paper/paper.qmd
changed table2 formatting

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
library(stargazer)
library(kableExtra)
```

@@

#kable(organized_table_2, "latex", booktabs = TRUE, caption = "Summary Statistics for My Data") %>%
#  kable_styling(latex_options = c("striped", "hold_position"))
organized_table_2

```

>>>>

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
library(stargazer)
library(kableExtra)
library(gtsummary)
```

@@

```
```{r}
table_content <- readLines("~/Police-Award-Nomination-Paper-Reproduction/table_2.tex", warn = FALSE)

# Print the contents of the table
cat(table_content, sep = "\n")
```
